\documentclass{cosic-letter}

\begin{document}

\recipient{
Dr Helen Smith\\
Cryptography and Information Security Group,\\
77 Massachusetts Ave,\\
Cambridge, MA, United States
}

\datesubject
{Leuven, \today}
{Recommendation letter for dan Peel}

Dear Doctor, 

I am privileged to write in support of my dear friend and student, Dan Peel. Dan studied in my classroom and
laboratory program for close to three years, during which time I witnessed his tremendous growth and development. This
development came not only in the area of business achievement and leadership, but in maturity and character as well.

Dan entered Whitman at the young age of 16, a precocious high school graduate. At first, he had difficulty accepting his
place as a young, less experienced lab member. But soon, he learned the valuable trait of humility, and enjoyed the
opportunity to learn from his older peers and his professors.

Dan quickly learned to manage his time, work in group situations under strict deadlines, and to recognize the importance
of a strong work ethic, persistence, and intellectual integrity. He has long since become the most valuable member of
my student-lab team, and a role model for his newer classmates.

I recommend Dan to your fellowship program with absolute confidence. He has made me proud, as his teacher and friend,
and I am sure will continue to do so as he grows in your business program and beyond.

Thank you for the opportunity of correspondence,

Sincerely,

\signature{Dr. Antoon Bosselaers,\\Professor, Whiteman}


\end{document}
